---
name: Matthias
surname: Grenié
position: "Postdoctoral Researcher"
address: "German Centre for Integrative Biodversity Research (iDiv), Halle-Jena-Leipzig"
phone: +49 341 9733176
csl: proceedings-of-the-royal-society-b.csl
orcid: 0000-0002-4659-7522
www: rekyt.github.io
email: "matthias.grenie@idiv.de"
twitter: LeNematode
github: Rekyt
scholar: "fZ1_d7QAAAAJ"
researchgate: Matthias-Grenie
date: "`r withr::with_locale(c(LC_TIME = 'en_US'), {format(Sys.time(), '%B %Y')})`"
output:
  vitae::hyndman
header-includes:
  \definecolor{headcolor}{HTML}{1E49BF}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Scientific Education

```{r acedemic-education}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "PhD in Ecology", "2016-2020", "CEFE, Montpellier University", "Montpellier, France",
  c("Supervised by \\textbf{Dr. Cyrille Violle} and \\textbf{Pr. Françoiz Munoz}.",
    "PhD title: 'Outside the norm: deviation from ecological optimality and functional originality'"),
  "MSc. in General Biology", "2013-2015", "École Normale Supérieure de Lyon", "Lyon, France", NULL,
  "Bsc. in General Biology", "2012-2013", "École Normale Supérieure de Lyon", "Lyon, France", NULL
) %>% 
  detailed_entries(Degree, Year, Institution, Where, why = Why, .protect = FALSE)
```

# Academic Experience

```{r academic-experience}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "Postdoctoral Researcher", "Oct. 2020-\\textbf{now}", "German Center for Integrative Biodiversity Research iDiv / Leipzig University", "Leipzig, Germany",
  c("Working with \\textbf{Dr. Marten Winter} on the functional biogegraphy of alien plants"),
  "PhD Student", "2016-2020", "Montpellier University", "Montpellier, France", NULL,
  "Master Intern", "Feb. 2015-June 2015", "EcoFOG", "Kourou, French Guiana, France",
  "Supervised by \\textbf{Dr. Bruno Hérault} on intraspecific variability in tropical trees growth in function of functional traits",
  "Master Intern", "Sept. 2014-Dec. 2014", "ISEM, University of Montpellier", "Montpellier, France",
    "Supervised by \\textbf{Dr. Ophélie Ronce} on matrix population models",
  "Master Intern", "Feb. 2014-July 2014", "Indiana University", "Bloomington, IN, USA",
    "Supervised by \\textbf{Dr. Jean-François Goût} in Michael Lynch's lab on trait motifs in the *Paramecium* complex"
) %>% 
  detailed_entries(Degree, Year, Institution, Where, why = Why, .protect = FALSE)
```

# Scientific Supervision

Master students supervision. Charlotte & Nathan.


# Scientific Service

Elected Lab council, peer reviews for XX and YY journals,reviewer for rOpenSci, conference organization (MEE), half-day workshop on Open Science CEFE R User Group. Organize sDiv lab meetings. PhD Advisory Committee.


# Scientic Projects

Active member of FREE CESAB group, GloNAF, Impacts CESAB group.


# Scientific Contributions

## Publications

```{r published-papers}
library(dplyr)

papers = bibliography_entries("papers.bib")

papers %>%
  arrange(issued)
```

## Conference Proceedings

```{r conf-proc}
bibliography_entries("conference_proceedings.bib")
```

## R Packages

          Name                      Description    Status
-------------- -------------------------------- ---------
`funrar`       computes functional originality  on GitHub
`ecolottery`   bla                              test
`rtaxref`      bla                              test
`rromeo`       bla                              test
`fundiversity` bla                              test
`funbiogeo`    bla                              test

* **`funrar`**computes functional originality indices central for CESAB FREE group analyses, [published paper], [CRAN link](https://cran.r-project.org/package=funrar), [GitHub link](https://github.com/Rekyt/funrar)
* **`ecolottery`** simulates community assembly processes cleverly with both niche and neutral processes, [published paper], [CRAN link](https://cran.r-project.org/package=ecolottery), [GitHub link](https://github.com/frmunoz/ecolottery)
* **`rtaxref`** accesses the French Taxonomic Referential (TAXREF) API, [GitHub link](https://github.com/Rekyt/rtaxref)
* **`rromeo`** accesses the Sherpa/RoMEO API on Open Access journals, reviewed by rOpenSci, [CRAN link](https://cran.r-project.org/package=rromeo), [GitHub link](https://github.com/ropensci/rromeo)
* **`fundiversity`** is a fast and modular package to compute functional diversity indices, [CRAN link](https://cran.r-project.org/package=fundiversity), [GitHub link](https://github.com/bisaloo/fundiversity)
* **`funbiogeo`** helps to create functional biogeography workflows, developed in the context of the FREE CESAB group, [GitHub link](https://github.com/FRBCesab/funbiogeo)
* Contributions to several biodiversity packages: [**`taxize`**](https://cran.r-project.org/package=taxize)

## Invited Talks

Göttingen lab seminar, D2KAB workshop.

## Talks

## Blogposts

```{r blogposts}
bibliography_entries("blogposts.bib")
```


# Teaching

Summary table. Year, Institution, Name of course, role, number of students.


# Skills

## Languages

French, English, Spanish, German, Chinese, Japanese

## Programming languages

R practices, data visualization, spatial data, SQL, HPC, git + GitHub collaborative development.
