---
name: Matthias
surname: Grenié
position: "Postdoctoral Researcher"
address: "German Centre for Integrative Biodversity Research (iDiv), Halle-Jena-Leipzig"
phone: +49 341 9733176
orcid: 0000-0002-4659-7522
www: rekyt.github.io
email: "matthias.grenie@idiv.de"
twitter: LeNematode
github: Rekyt
scholar: "fZ1_d7QAAAAJ"
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::hyndman
header-includes:
  \definecolor{headcolor}{HTML}{1E49BF}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Scientific Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Informal studies", "1889-91", "Flying University", "Warsaw, Poland",
  "Master of Physics", "1893", "Sorbonne Université", "Paris, France",
  "Master of Mathematics", "1894", "Sorbonne Université", "Paris, France"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```


# Scientific Supervision

Master students supervision. Charlotte & Nathan.


# Scientific Service

Elected Lab council, peer reviews for XX and YY journals,reviewer for rOpenSci, conference organization (MEE), half-day workshop on Open Science CEFE R User Group. Organize sDiv lab meetings. PhD Advisory Committee.


# Scientic Projects

Active member of FREE CESAB group, GloNAF, Impacts CESAB group.


# Scientific Contributions

## Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")
bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

## Preprints

## R Packages

List of R packages, which are on CRAN, peer-reviewed, explanation

## Invited Talks

Göttingen lab seminar, D2KAB workshop.

## Talks

## Blogposts

2 blogposts for rOpenSci. 1 blogspot for MEE.


# Teaching

Summary table. Year, Institution, Name of course, role, number of students.


# Skills

## Languages

French, English, Spanish, German, Chinese, Japanese

## Programming languages

R practices, data visualization, spatial data, SQL, HPC, git + GitHub collaborative development.
